Determining the alternatives for scalar implicature

### 2016-01-27 Paper/Paper.Rmd
changed literal semantics plot. have first version of pragmatic lisetner plot (only showing top scalar items

```{r helpers}
normedVec <- function(vec) vec / sum(vec)
```

@@

# Experiments E8, E10, E12: Literal listener
# ------------------------------------------
speakerE12 <- read.csv("../models/model_data/L0_e12.csv", stringsAsFactors = FALSE)
speakerE10 <- read.csv("../models/model_data/L0_e10.csv", stringsAsFactors = FALSE)
speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
# Experiments E6, E11: Pragmatic listener
# ---------------------------------------
listenerE6 <- read.csv("../models/model_data/L1_e6.csv", stringsAsFactors = FALSE)
listenerE11 <- read.csv("../models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
```

```{r}
listeners <- bind_rows(listenerE6 %>% mutate(expt = "1b"), 
                      listenerE11 %>% mutate(expt = "3b"))
zeros <- expand.grid(degree = c("low","hi"), 
            scale = unique(listeners$scale), 
            stars = 1:5, 
            expt = c("1b","3b"))

zlisteners <- full_join(listeners, zeros) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p))

# ggplot(zlisteners, 
#        aes(x = stars, y = listener.p, col = degree, lty = expt)) + 
#   geom_line() + 
#   facet_grid(. ~ scale) + 
#   theme_bw()
# Humpty Dumpty Quote...
```
# Introduction

@@

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup. Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star-rating. Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank. Each participant saw all scalar item and star rating combinations for their particular condition (see Figure \ref{fig:allScalesTable}), in a random oder.

@@

```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a, 3a, and 4. Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).  Each panel shows one scalar pair."}

speakers <- bind_rows(speakerE12 %>% mutate(expt = "4"), 
                      speakerE10 %>% mutate(expt = "3a"), 
                      speakerE8 %>% mutate(expt = "1a"))

ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = degree, lty = expt)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
                               title = "Scalar Item"), 
         linetype = guide_legend(direction = "horizontal", nrow = 1, 
                                 title = "Experiment")) + 
  xlab("Star Rating") +
  ylab("Proportion Judgments") + 
  # scale_colour_solarized() + 
  theme_bw() + 
  theme(legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"))
```

@@

# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
  geom_bar(stat="identity") + 
  ylim(0, 52) + 
  labs(x = "alternative", y = "counts") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
  ylab("Proportion of responses")
```

@@

>>>>

```{r helpers}
# lookupScalar()
# --------------
# degree :: scale degree ("hi", "low", "hi2" "h1", etc)
# scale  :: "some_all", "good_excellent"...
# exp    :: exp ide (e12, e8)
lookupScalar <- function(degree, scale, exp) {
  if (scale == "some_all") {
    if (exp == "e12") {
      if (degree == "hi1") return("all")
      if (degree == "hi2") return("most")
      if (degree == "mid") return("some")
      if (degree == "low1") return("little")
      if (degree == "low2") return("none")
    } else if (exp == "e10" | exp == "e11") {
      if (degree == "hi1") return("all")
      if (degree == "hi2") return("most")
      if (degree == "low1") return("some")
      if (degree == "low2") return("none")
    } else { ## must be exp 8
      if (degree == "hi") return("all")
      if (degree == "low") return("some")
    }
  # liked_loved
  } else if (scale == "liked_loved") {
    if (degree == "hi1" | degree == "hi") return("loved")
    if (degree == "hi2" | degree == "low") return("liked")
    if (degree == "mid") return("indifferent")
    if (degree == "low1") return("disliked")
    if (degree == "low2") return("hated")
  # good_excellent
  } else if (scale == "good_excellent") {
    if (degree == "hi1" | degree == "hi") return("excellent")
    if (degree == "hi2" | degree == "low") return("good")
    if (degree == "mid") return("okay")
    if (degree == "low1") return("bad")
    if (degree == "low2") return("horrible")
  # paltable_delicious
  } else if (scale == "palatable_delicious") {
    if (degree == "hi1" | degree == "hi") return("delicious")
    if (degree == "hi2" | degree == "low") return("palatable")
    if (degree == "mid") return("mediocre")
    if (degree == "low1") return("gross")
    if (degree == "low2") return("disgusting")
  # memorable_unforgettable
  } else if (scale == "memorable_unforgettable") {
    if (degree == "hi1" | degree == "hi") return("unforgettable")
    if (degree == "hi2" | degree == "low") return("memorable")
    if (degree == "mid") return("ordinary")
    if (degree == "low1") return("bland")
    if (degree == "low2") return("forgettable")
  }
  NA
}

normedVec <- function(vec) vec / sum(vec)
```

@@

# Experiments E8, E10, E12: Literal listener
# ------------------------------------------
speakerE12 <- read.csv("../models/model_data/L0_e12.csv", stringsAsFactors = FALSE)
speakerE10 <- read.csv("../models/model_data/L0_e10.csv", stringsAsFactors = FALSE)
# speakerE8 <- read.csv("../models/model_data/L0_e8.csv", stringsAsFactors = FALSE)
speakerE8 <- read.csv("../models/model_data/L0_e8Compliance.csv", stringsAsFactors = FALSE)
# Experiments E6, E11: Pragmatic listener
# ---------------------------------------
listenerE6 <- read.csv("../models/model_data/L1_e6.csv", stringsAsFactors = FALSE)
listenerE11 <- read.csv("../models/model_data/L1_e11.csv", stringsAsFactors = FALSE)
```

# Humpty Dumpty Quote...
# Introduction

@@

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup. Participants were presented with a target scalar item and a star rating (1--5 stars) and asked to judge the compatibility of the scalar item and star rating. Compatibility was assessed through a binary "yes/no" response to a question of the form "Do you think that the person thought the food was \____?" where a target scalar was presented in the blank. Each participant saw all scalar item and star rating combinations for their particular condition (see Figure \ref{fig:allScalesTable}), in a random oder.

@@

```{r exp1Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=5, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Literal listener judgements from Experiments 1a, 3a, and 4. Proportion of participants indicating acceptability is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the different items in the scale (with the experiments including different numbers of items).  Each panel shows one scalar pair."}

speakers <- bind_rows(speakerE12 %>% mutate(expt = "e12"), 
                      speakerE10 %>% mutate(expt = "e10"), 
                      speakerE8 %>% mutate(expt = "e8"))
speakers$scale <- as.factor(speakers$scale)

speakers$word <- as.factor(with(speakers, mapply(lookupScalar, degree, scale, expt)))
speakers$wordPlots <- factor(speakers$word, levels=c("excellent", "good", "okay", "bad", "horrible",
                           "loved", "liked", "indifferent", "disliked", "hated",
                           "unforgettable", "memorable", "ordinary", "bland", "forgettable",
                           "delicious", "palatable", "mediocre", "gross", "disgusting",
                           "all", "most", "some", "little", "none"))

# change col = word and facet_grid(.~scale)
ggplot(speakers, 
       aes(x = stars, y = speaker.p, col = scale, lty = expt)) + 
  geom_line() + 
  # facet_grid(.~ scale) + 
  facet_wrap(~wordPlots) +
  guides(colour = guide_legend(direction = "horizontal", nrow = 1, 
                               title = "Scalar Item"), 
         linetype = guide_legend(direction = "horizontal", nrow = 1, 
                                 title = "Experiment")) + 
  xlab("star rating") +
  ylab("Proportion compatible") + 
  ggtitle("Scalar item literal semantic compatibility\nwith star ratings") +
  # scale_colour_solarized() + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 8),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        axis.text.x = element_text(size = 8),
        axis.text.y = element_text(size = 6))
```

@@

# plotData <- head(plotData[order(plotData$n, decreasing = TRUE),], n = 24)
ggplot(data = plotData, aes(x = reorder(alt, -n), y = n)) +
  geom_bar(stat="identity") + 
  ylim(0, 52) + 
  labs(x = "Alternatives", y = "Counts") +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5)) + 
  theme_bw() +
  theme(strip.text.x = element_text(size = 8),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = .5, size = 6),
        axis.text.y = element_text(size = 10))
```

@@

```{r exp2Plots, fig.env = "figure*", fig.pos = "t", fig.width=6.5, fig.height=3, fig.align='center', set.cap.width=T, num.cols.cap=2, fig.cap = "Pragmatic listener judgements for our entailment scalar items. Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale. Each panel shows one scalar pair."}
# Get zero's in data frame
baseDf <- data.frame(degree = rep(c("hi", "low", "hi1", "hi2", "low1", "low2"), 25),
                     scale = c(rep("good_excellent", 6 * 5),
                               rep("liked_loved", 6 * 5),
                               rep("memorable_unforgettable", 6 * 5),
                               rep("palatable_delicious", 6 * 5),
                               rep("some_all", 6 * 5)),
                     stars = rep(1:5, 30),
                     combine = rep(TRUE, 150))
listeners <- bind_rows(listenerE6 %>% mutate(expt = "e6"), 
                      listenerE11 %>% mutate(expt = "e11"))
listeners <- left_join(baseDf, listeners) %>%
  mutate(listener.p = ifelse(is.na(listener.p), 0, listener.p),
         expt = ifelse(degree == "hi" | degree == "low", "e6", "e11"))
listeners$word <- as.factor(with(listeners, mapply(lookupScalar, degree, scale, expt)))
listeners$plotThis <- with(listeners, ifelse(scale == "some_all" &
                               (degree == "hi" | degree == "low" | degree == "hi1" | degree == "low1"),
                               TRUE, ifelse(scale != "some_all" & (
                                 degree == "hi" | degree == "low" | degree == "hi1" | degree == "hi2"),
                                 TRUE, FALSE)))
listeners$scalarType <- with(listeners, ifelse(degree == "hi" | degree == "hi1", "stronger", "weaker"))

# Plot pragmatic listener data here
ggplot(subset(listeners, plotThis == TRUE),
       aes(x = stars, y = listener.p, col = scalarType, lty = expt)) + 
  geom_line() + 
  facet_grid(.~ scale) + 
  ggtitle("Pragmatic listener judgments") +
  ylab("Proportion of stars selected") +
  xlab("Star rating") +
  theme_bw() +
  theme(strip.text.x = element_text(size = 6),
        legend.position = "bottom",
        legend.margin = unit(.02,"in"),
        legend.key = element_blank(), 
        legend.key.size = unit(.1, "in"),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 8))
```

### 2016-01-27 Paper/Paper.tex
changed literal semantics plot. have first version of pragmatic lisetner plot (only showing top scalar items

@@

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
Participants were presented with a target scalar item and a star rating
(1--5 stars) and asked to judge the compatibility of the scalar item and
star-rating. Compatibility was assessed through a binary ``yes/no''
response to a question of the form ``Do you think that the person
thought the food was \_\_\_\_?" where a target scalar was presented in
the blank. Each participant saw all scalar item and star rating
combinations for their particular condition (see Figure
\ref{fig:allScalesTable}), in a random oder.

@@

>>>>

\section{Humpty Dumpty Quote\ldots{}}\label{humpty-dumpty-quote}

@@

Figure \ref{fig:stimuli_exp1}, left, shows the experimental setup.
Participants were presented with a target scalar item and a star rating
(1--5 stars) and asked to judge the compatibility of the scalar item and
star rating. Compatibility was assessed through a binary ``yes/no''
response to a question of the form ``Do you think that the person
thought the food was \_\_\_\_?" where a target scalar was presented in
the blank. Each participant saw all scalar item and star rating
combinations for their particular condition (see Figure
\ref{fig:allScalesTable}), in a random oder.

@@

{\centering \includegraphics{figs/exp2Plots-1}

\caption[Pragmatic listener judgements for our entailment scalar items]{Pragmatic listener judgements for our entailment scalar items. Proportion of participants generating a star rating is shown on the vertical axis, with the horizontal axis showing number of stars on which the utterance was judged. Each line-type shows a different experiment, and colors indicate the stronger (ie excellent) or weaker (ie good) scalar items for each scale. Each panel shows one scalar pair.}\label{fig:exp2Plots}
\end{figure*}
\end{CodeChunk}
